Cognitive Context: Impact on the Perception of a Robot

### 2015-07-02 main.tex
Formula for gaze difference
Updated title

\rightheader{Impact of Cognitive Context in the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Impact of Context in the Perception of a Robot}

@@

\subsection{Impact of the tendency to anthropomorphize on the robot \vs human
gazing behaviours}

>>>>

\rightheader{Cognitive Context: Impace on the Perception of a Robot}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Cognitive Context: Impact on the Perception of a Robot}

@@

\subsection{Impact of the tendency to anthropomorphize on human
gazing behaviours}
